Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2017-11-28 hpmoon-asoco.tex
Addressing @julioortega final comments

One of the most extended methods to deal with high-dimensional multi-objective optimization problems are the distributed co-evolutionary algorithms. In these methods each processor deals only with a part of the decision space, that is, the individuals belonging to the same sub-population (island) explore the same subset of decision variables. However, only decomposable problems could be strictly implemented in parallel this way. A new approach is presented here to deal with un-decomposable problems, the selective operator application: instead of sharing parts of individuals, each processor applies the variation operators to a specific subset of the whole individual. We have previously proved that extending the length of these subsets, and therefore, sharing some search space between islands, implies an improvement in the results. Specifically, in this paper, a new method to automatically adapt the size of the overlapping, or shared sections, of the individuals has been compared to other collaborative evolutionary techniques. Different number of islands, chromosome sizes and problems have been used. The analysis of the obtained experimental results, by using different metrics, shows that our approach can provide statistically significant improvements with respect to the base algorithm.  Results also show that the relation between the number of islands (subpopulations) and the length of the chromosome (number of decision variables) is also a relevant factor to determine the most efficient alternative to distribute the decision variables. 
\end{abstract}

@@

\subsubsection{Adaptive SLA with overlapping islands (A)} 
As in the previous method, the sections to address by the operators are overlapped, but
instead of using one extra section on each side of the $p$ section ($p+1$
and $p-1$), it uses $c$ fragments on each side ($p+c$ and $p-c$),
being $c$ a value depending on the number of islands.
% That's not adaptive. It's simply variable - JJ FERGU: it depends on the number of islands. What term do you suggest?
As a first
approach to automatically calculate this value, the results shown in
\citep{Garcia16hpmoon} have been used as a base to obtain $c$. In that
work, the overlapped method ($c=1$) obtained better results when the
number of islands were $>$8. On the contrary, when the number of
islands is small, no overlapping is necessary. So, we have used this
knowledge to create the formula $c=round(0.2*P-1)/2$ to calculate the
extra sections to overlap. Therefore, when $P=8$ then $c=0$
(equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so
on. As mentioned, this is only a first approach to obtain $c$, and future work will study new methods to calculate it. Figure \ref{fig:adaptive} explains this method.

>>>>

One of the most extended methods to deal with high-dimensional multi-objective optimization problems are the distributed co-evolutionary algorithms. In these methods each processor deals only with a part of the decision space, that is, the individuals belonging to the same sub-population (island) explore the same subset of decision variables. However, only decomposable problems could be strictly implemented in parallel this way. A new approach is presented here to deal with un-decomposable problems, the selective operator application: instead of sharing parts of individuals, each processor applies the variation operators to a specific subset of the whole individual. We have previously proved that extending the length of these subsets, and therefore, sharing some search space between islands, implies an improvement in the results. Specifically, in this paper, a new method to automatically adapt the size of the overlapping, or shared sections, of the individuals has been compared to other collaborative evolutionary techniques considering different number of islands, chromosome sizes and benchmarks. The analysis of the obtained experimental results, by using different metrics, shows that our approach can provide statistically significant improvements with respect to the base algorithm.  Results also show that the relation between the number of islands (subpopulations) and the length of the chromosome (number of decision variables) is also a relevant factor to determine the most efficient alternative to distribute the decision variables.

\end{abstract}

@@

\subsubsection{Adaptive SLA with overlapping islands (A)} 
As in the previous method, the sections to address by the operators are overlapped, but
instead of using one extra section on each side of the $p$ section ($p+1$
and $p-1$), it uses $c$ fragments on each side ($p+c$ and $p-c$),
being $c$ a value depending on the number of islands.
% That's not adaptive. It's simply variable - JJ FERGU: it depends on the number of islands. What term do you suggest?
As a first
approach to automatically calculate this value, the results shown in
\citep{Garcia16hpmoon} have been used as a base to obtain $c$. In that
work, the overlapped method ($c=1$) obtained better results when the
number of islands were bigger than 8. On the contrary, when the number of
islands is small, no overlapping is necessary. So, we have used this
knowledge to create the formula $c=round(0.2*P-1)/2$ to calculate the
extra sections to overlap. Therefore, when $P=8$ then $c=0$
(equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so
on. As mentioned, this is only a first approach to obtain $c$, and future work will study new methods to calculate it. Figure \ref{fig:adaptive} explains this method.
